A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 1_intro.tex
redo all accuracy and width figures

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}

>>>>

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_accuracy.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}

### 2019-08-23 5_generalization.tex
redo all accuracy and width figures

\subsection{Beading strategies}
We introduce several beading strategies which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.

@@

\begin{figure}
\centering
\setlength{\figwidth}{.45\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
}
\label{distributed_comparison}
\end{figure}

>>>>

\subsection{Beading strategies}
We introduce several beading strategies which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading strategies.
We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.

@@

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}
